---
title: "Visualize Data"
---

## Your Turn 0

Add a setup chunk that loads the tidyverse packages.



```{r}
dementia <- readRDS(here::here("data/dementia.Rds"))
```


## Your Turn 1

Run the code on the slide to make a graph. Pay strict attention to spelling, capitalization, and parentheses!

```{r}

```

## Your Turn 2

Add `color`, `size`, `alpha`, and `shape` aesthetics to your graph. Experiment.  

```{r}
ggplot(data = dementia) +
  geom_point(mapping = aes(x = age, y = QoL))
```

## Your Turn 3

Add the highlighted code to your graph. What does it do?

```{r}
ggplot(data = dementia) +
  geom_point(mapping = aes(x = age, y = QoL))
```

## Your Turn 4

Replace this scatterplot with one that draws boxplots. Use the cheatsheet. Try your best guess.

```{r}
ggplot(data = dementia) +
      geom_point(mapping = aes(x = mmse, 
                               y = QoL))
```

## Your Turn 5

Make a histogram of the `stay` variable from `dementia`. Hint: do not supply a y variable.

```{r}

```

## Your Turn 6

Make a bar chart for `mmse` with coloured bars according to the the type of dementia. Use the help page for `geom_bar` to choose a "color" aesthetic for class.

```{r}

```

## Your Turn 7

- Save your last plot and then locate it in your files pane 
- Download it (you may have to refresh the files list)

## Your Turn 8

Run esquisse::esquisser() in the console and use it to create a bar chart of the number of patients who sustained a fall. Export the code to produce the plot into the chunk below so that you can reproduce it more easily. 

```{r}

```

## Your Turn 9

**Modify the code below to:**

- Show participants characteristics by those who did or did not sustatin a fall
- Include the number of hospitalizations in the past year as a rows
- Download the table

```{r}
library(gtsummary)

dementia %>% 
  select(age, sex, stay, braden,
         QoL, pain, pas, physres, chemicalres, fall,
         mmse) %>% 
  tbl_summary(by = mmse,
    statistic = list(all_continuous() ~ "{mean} ({sd})"),
    type = list(pain ~ "continuous"),
     missing = "no"
              )%>%
  italicize_labels()
```


# Take away

You can use this code template to make thousands of graphs with **ggplot2**.

```{r eval = FALSE}
ggplot(data = <DATA>) +
  <GEOM_FUNCTION>(mapping = aes(<MAPPINGS>))
```