---
title: "Transform Data"
---

```{r setup}
library(tidyverse)
```

# Import Data

## Your Turn 1

- Download a csv or excel file (your choice) of the dementia dataset from the workshop webpage
- Upload it to RStudio cloud into a new folder called 'data'
- Import the data set using the GUI (name the dataset `dementia`).
- Try the code approach (below) to importing data with the here package for 'safe' file paths.

```{r}
# don't forget to 
#dementia <- read_csv(here::here("data","dementia.csv"))
#dementia <- readxl::read_excel(here::here("data", "dementia.xlsx"))
```

# dplyr

## Your Turn 2

Alter the code to select just the `mmse` column:

```{r }
select(dementia, id, age) 
```

## Your Turn 3

Use `filter`, `dementia`, and the logical operators to find:

- All of the patients where length of stay is greater than or equal to 5
- All of the patients who had both chemical *and* physical restraints


```{r}

```

## Your Turn 4

Use `%>%` to write a sequence of functions that: 

1. Filters mmse to just the patients with mild dementia, *then...*  
2. Selects the quality of life and number of hospitalizations columns, *then...*  

```{r}
```

## Your Turn 5

Use `mutate()` and `case_when` to create a variable called stay_category that assigns length of stay into the categories 'short' (1-3 days), 'moderate' (4-8 days) and 'long' (>8 days).

*(Hint: Be sure to remove each `_` before running the code)*

```{r}
dementia <- dementia %>% 
  ______(stay_category = case_when(stay < _ ~ "short",
                                   stay < _ & ___ > _ ~ "moderate",
                                   ___ _ _ ~ ___)
         )

# check your result
dementia %>% 
  select(stay, stay_category)
```


## Your Turn 6

Complete the code below to extract the rows where `chemicalres == "yes"`. Then use `summarise()` and `sum()` and `min()` to find:

1. The total number of females
2. The lowest number of hospitalisations

*(Hint: Be sure to remove each `_` before running the code)*

```{r}
dementia ___ 
  filter(_______________________) ___
  ___________(total_female = ________, shorted_hospitalisation = _______)

```

## Your Turn 7

- Install the `infer` package by running `install.packages("infer")` in the console.
- Load the `infer` package so you can use its functions
- Use a t test to determine if length of stay is associated with sustaining a fall whilst in hospital

```{r}

```

# Take aways

* Extract variables with `select()`  
* Extract cases with `filter()`  

* Make tables of summaries with `summarise()`  
* Make new variables, with `mutate()`  

* Connect operations with `%>%`  


